Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by \textsc{DigitalSnow} ANR-11-BS02-009, \textsc{KIDICO} ANR-2010-BLAN-0205 and \textsc{PRIMES Labex} ANR-11-LABX-0063/ ANR-11-IDEX-0007 research grants.}

### 2015-10-23 latex/article.tex
figs

\begin{figure}
  \begin{center}
    \subfigure[]{\includegraphics[width=4cm]{figs/approx1}}
    \subfigure[]{\includegraphics[width=4cm]{figs/approx-reg-1}}
    \subfigure[]{\includegraphics[width=4cm]{figs/approx-reg-2}}
  \end{center}
  \caption{Integral computation with an area estimation from pixel
    counting $(b)$ or from densities (represented by different
    gray values) in a mipmap approximation of $\Shape$.}
  \label{fig:approx}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \subfigure[]{\includegraphics[width=4cm]{figs/approx-bh}}
    \subfigure[]{\includegraphics[width=4cm]{figs/approx-ada}}
  \end{center}
  \caption{Adaptive approximation of the integration using a
    hierarchical decomposition of the ball $\Ball{R}{\vx}$ $(a)$, or a decomposition of $\Ball{R}{\vx}\cap\Shape$.}
  \label{fig:approx2}
\end{figure}

@@

\begin{figure}
  \begin{center}
    {\includegraphics[width=2.7cm]{figs/EG_dragon_mean}}
    {\includegraphics[width=2.7cm]{figs/EG_dragon_gaussian}}
    {\includegraphics[width=2.7cm]{figs/EG_dragon_k1}}
    {\includegraphics[width=2.7cm]{figs/EG_dragon_k2}}\\
    {\includegraphics[width=2.7cm]{figs/EG_dragon_normal_zoom}}
    {\includegraphics[width=2.7cm]{figs/EG_dragon_dir_min_zoom}}
    {\includegraphics[width=2.7cm]{figs/EG_dragon_dir_max_zoom}}\\
    {\includegraphics[width=2.2cm]{figs/function_mean_0}}
    {\includegraphics[width=2.2cm]{figs/function_mean_1}}
    {\includegraphics[width=2.2cm]{figs/function_mean_2}}
    {\includegraphics[width=2.2cm]{figs/function_mean_3}}
    {\includegraphics[width=2.2cm]{figs/function_mean_4}}
  \end{center}
  \caption{Illustration fig illustration complete (adaptative, ...) plusieurs
    objets.. + dynamique.
    %
    \emph{Third row:} mean curvature computed in real-time on a dynamic object.}
  \label{fig:full}
\end{figure}

>>>>

\begin{figure}
  \begin{center}
    {\includegraphics[width=4cm]{figs/approx1}}
    {\includegraphics[width=4cm]{figs/approx-reg-1}}
    {\includegraphics[width=4cm]{figs/approx-reg-2}}
  \end{center}
  \caption{Integral computation with an area estimation (\emph{left}) from pixel
    counting (\emph{middle}) or from densities (represented by different
    gray values) in a mipmap approximation of $\Shape$ (\emph{right}).}
  \label{fig:approx}
\end{figure}

@@

\begin{figure}
  \begin{center}
    {\includegraphics[width=4cm]{figs/approx-bh}}
    {\includegraphics[width=4cm]{figs/approx-ada}}
  \end{center}
  \caption{Adaptive approximation of the integration using a
    hierarchical decomposition of the ball $\Ball{R}{\vx}$ (\emph{left}), or a decomposition of $\Ball{R}{\vx}\cap\Shape$ (\emph{right}).}
  \label{fig:approx2}
\end{figure}

@@

\begin{figure}
  \begin{center}
    {\includegraphics[width=2.7cm]{figs/EG_dragon_mean}}
    {\includegraphics[width=2.7cm]{figs/EG_dragon_gaussian}}
    {\includegraphics[width=2.7cm]{figs/EG_dragon_k1}}
    {\includegraphics[width=2.7cm]{figs/EG_dragon_k2}}\\
    {\includegraphics[height=2.0cm]{figs/EG_dragon_normal_zoom}}
    {\includegraphics[height=2.0cm]{figs/EG_dragon_dir_min_zoom}}
    {\includegraphics[height=2.0cm]{figs/EG_dragon_dir_max_zoom}}
    {\includegraphics[height=2.0cm]{figs/snow_I08iso_233_r20_l0_m3}}\\
    {\includegraphics[width=2.2cm]{figs/function_mean_0}}
    {\includegraphics[width=2.2cm]{figs/function_mean_1}}
    {\includegraphics[width=2.2cm]{figs/function_mean_2}}
    {\includegraphics[width=2.2cm]{figs/function_mean_3}}
    {\includegraphics[width=2.2cm]{figs/function_mean_4}}
  \end{center}
  \caption{Illustration fig illustration complete (adaptative, ...) plusieurs
    objets.. + dynamique.
    %
    \emph{Third row:} mean curvature computed in real-time on a dynamic object.}
  \label{fig:full}
\end{figure}
